Toward theories of deliberated preferences

### 2020-11-10 simple.tex
Clearer intro

By contrast, this difficulty of validation is much alleviated with descriptive approaches. Such approaches can be validated by comfronting their predictions to empirical data. When two descriptive theories disagree on their predictions, it is often possible to show that at least one of them is wrong with a suitable experiment. 
\commentYM{quelle différence avec les implications empiriques d'une théorie normative ?}
Alàs, descriptive approaches as currently existing in decision theory are not suitable to obtain valid prescriptions.

@@

	Two theories of \ac{DJ} are opposed on their prediction of the reflexive choice of a given set of individuals $I$ having to choose one alternative among $\alts$.
	The \emph{satisfycing} theory claims that any individual $i \in I$ ought to choose, and will reflectively choose, whichever alternative is satisfying (and be indifferent if they are both satisfying or if none of them is). An alternative $\alt$ is satisfying iff $g_1(\alt) < t_1 \land g_2(\alt) > t_2$, where $t_1$ and $t_2$ are two real numbers chosen by the theorist.
	The \emph{additive} theory claims that any individual $i \in I$ ought to choose, and will reflectively choose, whichever alternative $\alt$ maximises $v(\alt) = v_1(g_1(\alt)) + v_2(g_2(\alt))$, where $v_i: \R → \R$ are functions  chosen by the theorist.
	How the parameters of these theories, $t_i$ and $v_i$, are determined is irrelevant to the questions tackled in this article, because it aims at defining and studying theories of \ac{DJ} in general, not at proposing a way of building a specific theory of \ac{DJ}. %For this example, one can assume that these parameters are determined on the basis of observation of the behavior of some population in some similar circumstances.

	Assume that the theories disagree, thus, that $\alt_1$ is satisfying and $\alt_2$ is not (say, it fails on the speed criterion), but $v(\alt_2) > v(\alt_1)$. To determine which theory is right, it is insufficient to simply observe what an individual $i \in I$ effectively chooses. This would merely reflect her unreflective behavior. The approach adopted in this article to capture \acp{DJ} is to declare that the winning theory (if any) is the one that exhibit arguments able to systematically convince individuals that their proposed choice is to be adopted.
	The satisfycing theory could argue as follows: “$\alt_1$ is better than $\alt_2$, because it has a satisfactory price (lower than $t_1$, an acceptable price) and a satisfactory speed (higher than $t_2$, thus an acceptable performance); whereas $\alt_2$ is not satisfactory on the speed criterion”. 
	The additive theory could use the following argument: “$\alt_2$ is better than $\alt_1$, because $\alt_2$ is cheaper than $\alt_1$, and this more than compensates for its weaker performance in terms of speed”.

@@

This article is structured as follows.
\Cref{sec:approaches} defines more precisely what is meant here with normative and descriptive theories. These definitions permit to readily see why the apparent impossibility of a claim being both normative and descriptive is an illusion, thereby enabling a solution to what could be called the “normative against descriptive” gap. It also reviews related works in the literature, and briefly sketches the current proposal.
\Cref{sec:normative,sec:descriptive} define the theories of \ac{DJ} and prove that these theories are normative and descriptive in the sense defined in \cref{sec:approaches}. \Cref{sec:preferences} define theories of \ac{DP} on the basis of theories of \ac{DJ}, and \cref{sec:conclusion} concludes.

@@

A possible objection to the usefulness of this approach should perhaps be lifted before delving into the formal descriptions of this rough sketch.
It may be argued that because this proposition needs a normative axiom, which cannot be validated empirically, it does not fare better than the alternative propositions existing in the literature. \ac{SEU}, for example, also can be considered to claim to obtain reflective preferences on the basis of normative axioms.
I grant that it is impossible to get completely rid of normative axioms, because prescriptions must be linked to descriptions, and this cannot be done in a complete empirical way.
However, it is good to lighten as much as possible the content of normative axioms, and defer as much content as possible to descriptive claims. The descriptive parts of theories can be confronted to observations, a natural way to lift disagreements that has often proved useful in the history of science (again, accepting this claim does not require to ignore that observations themselves rest upon theories). Arguably, the normative axiom proposed here is much weaker than those of a theory such as \ac{SEU}, in the sense of having less substance. (This claim can only be valid at an intuitive level: because \ac{SEU} does not use arguments, its axioms cannot be compared formally to mine.) This does not prevent theories of \ac{DJ} to propose substantive, non-trivial claims about reflective preferences. It simply moves the debate from the world of discussions between experts about the validity of the axioms to the world of observations of acceptability of arguments by the persons to which these theories claim to be applicable.
It is also worth noting that the proposed axiom has a specific form that may permit decision makers to reconstruct the reasoning proposed by the theory so as to be able to check that they apply to their situation. Detailed exploration of this aspect is deferred to future work.

@@

\section{Descriptive theories}
\label{sec:descriptive}
\subsection{Informal presentation}
\commentOCf{Je ne me suis pas encore décidé : descriptive theory or empirical theory ? Pour le moment, j’utilise les deux expressions de façon interchangeable.}
A normative theory defines when a given argument is decisive for a given proposition and a given individual: whenever every sequence of arguments having that argument towards the end of the sequence lead the individual to adhere to the proposition. This, in turn, under condition of accepting its normative validity \commentYM{mais c'est quoi cette "normative validiy" ? de quelles conditions parles-tu ?}, permits in principle to know something about the \ac{DJ} of an individual. But this gives no concrete means to know someone’s \ac{DJ}. The set of finite sequence of arguments is infinite. The definition of decisiveness could admittedly be modified to account for an a priori bound on the maximal length of sequences, but this would not solve the practical problem that this set would be too large to be explored thoroughly 
\commentYM{certain que ce terme existe ?}
\commentOCf{Non, thoroughfully n’existe pas, en effet}. 
Furthermore, only some sequences of arguments can be tested for a given individual: the individual’s patience is limited. A supplementary problem might happen in some situations. Once a sequence has been presented to the individual, this cannot necessarily be undone: she might remember some of the arguments, and they may have a lasting influence on her perspective. Let me call this possibility the hypothesis of memory.
The converse hypothesis amounts to postulating that the individual forgets after some time and use an observation protocol that separates the tests in time sufficiently.
\commentYM{je comprends ce que tu veux dire ici car ça fait un bout de temps qu'on parle de ces question. Je doute cependant qu'un lecteur innocent comprenne un traitre mot}

Achieving knowledge of someone’s \ac{DJ} in practice is tackled by introducing empirical theories of \ac{DJ}. An empirical theory for a given normative theory defines a subset of propositions of the agenda, that it claims are contained in the \acp{DJ} of individuals concerned by the normative theory. They are called the proposition that the theory supports. \commentYM{dans la mesure où, à ce stade, je ne comprends pas bien ce que contient une "normative theory", la séparation avec l' "empirical theory" n'est pas claire pour moi} 
The theory also claims that it is able to argue in favor of the proposition it supports in such a way that individuals will be convinced of the quality of these arguments. This is accomplished by three binary relations, part of the definition of empiricial theories: one represents its initial arguments, one plans the possible attacks, and one defines its counter-arguments. An empirical theory also defines a concatenation operation able to dynamically build arguments from fragments of arguments.
The theory claims that when one of its arguments in support of one of its claims is unconvincing to an individual, it is because of one of the anticipated attacks; and the theory claims to be able to provide counter-arguments to such attacks as they come, that will in turn be either convincing to the individual, or fail to be because of some anticipated attack. The theory is also constrained to have “finite depth”, meaning that it must set an a priori limit to the number of such iterations of attacks and counter-arguments.

Thanks to these operators, an empirical theory may argue in a way that depends on the counter-arguments each individual finds appealing
\commentYM{je ne comprends pas cette phrase, et en particulier le sens qu'il faut donner au terme "adjust"}. Instead of having to give a single decisive argument in support of its claims, the theory may react to exactly the counter-arguments that a given individual thinks relevant.

Such theories satisfy the two properties that are mandatory to achieve what has been announced, namely, to obtain theories of \ac{DJ} whose power rest on a weak normative axiom and on empirically falsifiable claims. First, the main claim of the theory, of being able to argue convincingly, holds if and only if no falsification sequence exist. Second, granted normative adequacy, if indeed a theory is convincing, then it is valid, meaning that the proposition that it claims are \acp{DJ} are indeed \acp{DJ}. These two claims are laid out formally in \cref{th:svalid}.

A second goal of this section is to prove that when two theories disagree about incompatible propositions, one of the theories at least must fail some given series of empirical tests, which the proof describes. Importantly, these tests can be performed on a single individual and are robust against the hypothesis of memory.

\subsection{Definition}
In this section, a normative theory of \ac{DJ} $(\allprops, \allargs, I, {\allleadsto})$ is supposed given.
An empirical theory for a normative theory of \ac{DJ} is defined as a tuple $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$, where ${\gleadsto} \subseteq \allargs × \allprops$ is an initial argumentation relation; ${\gbeats} \subseteq \allargs × \allargs$ is an anticipated attacks relation; $\alldargs$ is a primitive set of argument fragments; ${\dbeats} \subseteq \alldargs × \gbeatsinv(\allargs)$ is a defense relation; and $+$ combines arguments to coalitions of fragments to form new arguments; with the supplementary constraint that the tuple must have a bounded depth. These concepts are now defined formally.
\commentYM{puisque la théorie empirique est une théorie empirique D'UNE CERTAINE THEORIE NORMATIVE, je m'attendrais  à ce qu'on voit apparaître la théorie normative dans la formule de la théorie empirique, non ?}

An initial argumentation relation ${\gleadsto} \subseteq \allargs × \allprops$ defines the set of supported  propositions and, for each supported propositions, the set of initial arguments for these propositions. 
More precisely, let $\gpropse$, the range of ${\gleadsto}$, be called the propositions supported by the descriptive theory.
Given such a supported proposition $\prop \in \gpropse$, let $\gleadstoinv(\prop) = \set{\ar \in \allargs \suchthat \ar \gleadsto \prop}$ be called the initial arguments in favor of $\prop$.

@@

A defense relation ${\dbeats} \subseteq \alldargs × \gbeatsinv(\allargs)$ is an injective (left-unique) and surjective (right-total) binary relation over $\alldargs × \gbeatsinv(\allargs)$. \commentYM{le fait qu'elle soit surjective et injective est une exigence que tu poses dans la définiton ? pourquoi ? à quoi est-ce que cela sert ?} 
These constraints guarantee that every anticipated attack has exactly one fragment defending against it, thus, $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton. 
Note that $\dbeats$ need not be a bijection as it is generally not a function (it is not restrictive to suppose it left-total, but it is generally not right-unique). 
Given $\ar_1 \in \gbeatsinv(\allargs)$, define $\dbeatsinv(\ar_1)$ as the fragment defending against the anticipated attack $\ar_1$.
\commentYM{dans toute cette sous-section la lecture est rendue très difficile par ce genre de formulation qui assigne une intentionnalité à la théorie. Je ne comprends pas le sens métaphorique de ces phrase, donc je ne les comprends pas}

@@

A \emph{coalition of fragments defending $\ar$} is any non-empty subset of $\df(\ar)$.
Such a coalition can be combined with the argument it defends to form a new argument.
An empirical theory defines, to that effect, a function $+: \allargs × \powersetz{\alldargs} → \allargs$.
Given any $\ar \in \allargs$ and $\emptyset ≠ \dargs \subseteq \alldargs$, the notation $\ar + \dargs$ stands for $+(\ar, \dargs)$. (The function $+$ need not be defined on so large a domain, because an argument is only ever added to its own defenders, but this definition is adopted for simplicity; \cref{sec:append} refines this requirement.)

>>>>

By contrast, this difficulty of validation is much alleviated with descriptive approaches. Such approaches can be validated by confronting their predictions to empirical data. When two descriptive theories disagree on their predictions, it is often possible to show that at least one of them is wrong with a suitable experiment. 
\commentYM{quelle différence avec les implications empiriques d'une théorie normative ?}
Alàs, descriptive approaches as currently existing in decision theory are not suitable to obtain valid prescriptions.

@@

	Two theories of \ac{DJ} are opposed on their prediction of the reflexive choice of a given set of individuals $I$ having to choose one alternative among $\alts$.
	The \emph{satisfycing} theory claims that any individual $i \in I$ ought to choose, and will reflectively choose, whichever alternative is satisfying (and be indifferent if they are both satisfying or if none of them is). An alternative $\alt$ is satisfying iff $g_1(\alt) < t_1 \land g_2(\alt) > t_2$, where $t_1$ and $t_2$ are two real numbers chosen by the theorist.
	The \emph{additive} theory claims that any individual $i \in I$ ought to choose, and will reflectively choose, whichever alternative $\alt$ maximises $v(\alt) = v_1(g_1(\alt)) + v_2(g_2(\alt))$, where $v_i: \R → \R$ are functions  chosen by the theorist.

	Assume that the theories disagree, thus, that $\alt_1$ is satisfying and $\alt_2$ is not (say, it fails on the speed criterion), but $v(\alt_2) > v(\alt_1)$. To determine which theory is right, it is insufficient to simply observe what an individual $i \in I$ effectively chooses. This would merely represent her unreflective behavior. The approach adopted in this article to capture \acp{DJ} is to declare that the winning theory (if any) is the one that exhibit arguments able to systematically convince individuals that their proposed choice is to be adopted.
	The satisfycing theory could argue as follows: “$\alt_1$ is better than $\alt_2$, because it has a satisfactory price (lower than $t_1$, an acceptable price) and a satisfactory speed (higher than $t_2$, thus an acceptable performance); whereas $\alt_2$ is not satisfactory on the speed criterion”. 
	The additive theory could use the following argument: “$\alt_2$ is better than $\alt_1$, because $\alt_2$ is cheaper than $\alt_1$, and this more than compensates for its weaker performance in terms of speed”.

@@

The important question about how the parameters $t_i$ and $v_i$ of these illustrative theories would be determined is left aside in this article. This article aims at defining and studying theories of \ac{DJ} in general, not at proposing a way of building a specific theory of \ac{DJ}. %For this example, one can assume that these parameters are determined on the basis of observation of the behavior of some population in some similar circumstances.

The approach it adopts is the following.
First, it introduces a normative axiom that mandates that whatever propositions the \ac{DM} accepts when reasoning carefully can be prescribed. This notion of careful acceptability is defined formally on the basis of an observable relation that captures the reactions of the \ac{DM} to arguments.
This requirement is described here as a normative axiom because it has to be accepted on the basis of its apparent adequacy to capture what is intuitively an acceptable requirement for a procedure aiming at prescribing to a \ac{DM}. In other words, it is not a hypothesis on the observable world: that the requirement holds cannot be proven by observation. It has, in that sense, a similar epistemological status as axioms of classical decision theories when they are applied for prescription, for example, Savage’s sure thing principle. Arguably, we can observe whether individuals unreflectively behave according to Savage’s sure thing principle, or any other decision-theoretic axiom, but even when they fail to, it can be said that this is because of a mistake: the normative status of an axiom is not hit by violations due to unreflective behavior. In that sense, such axioms are not falsifiable.

Second, this article defines descriptive theories of acceptable propositions. Acceptable here is in the sense of the careful acceptability just defined informally. Descriptive here means that these theories can predict at least some of the propositions that will be considered acceptable by the \ac{DM}.
This is arguably the more important and difficult part of the current research program: it has to convince that it is practically possible to define theories that predict such an a priori volatile thing as the way individuals reason. It is plain that mandating that theories be able to predict the reaction of individuals to every possible sequence of arguments they are exposed to would be plainly irrealistic. Some weaker criterion is required. How weak can it become? As announced, the proposed theories must be purely descriptive, apart from the required acceptance of the normative adequacy axiom described in the above paragraph. In other words, their conclusions must hold on the sole basis of the unique normative axiom, aided by claims that can be proven false experimentally. Equivalently, if the theory is invalid, in the sense of failing its predictions about the acceptability of propositions, then it must be falsifiable: there must exist a set of observable reactions of the \ac{DM} to arguments that contradict the claims of the theory. Accordingly, this article claims and proves that empirical theories of \ac{DJ} as defined here are such that under normative adequacy, if the theory is not falsified, then it is valid. I admit readily that this might not suffice to convince that building such concrete theories is feasible. It is only one of the difficulties to tackle.

A possible objection to the usefulness of this approach should perhaps be lifted before delving into the formal descriptions of this rough sketch.
It may be argued that because this proposition needs a normative axiom, which cannot be validated empirically, it does not fare better than the alternative propositions existing in the literature. 
%\ac{SEU}, for example, also can be considered to claim to obtain reflective preferences on the basis of normative axioms.
I grant that it is impossible to get completely rid of normative axioms, because prescriptions must be linked to descriptions, and this cannot be done in a complete empirical way.
However, it is good to lighten as much as possible the content of normative axioms, and defer as much content as possible to descriptive claims. The descriptive parts of theories can be confronted to observations, a natural way to lift disagreements that has often proved useful in the history of science (again, accepting this claim does not require to ignore that observations themselves rest upon theories). 
This article postulates that the normative axiom it proposes will be consensual, at least for some non trivial concrete instanciations of the proposed approach, among economists, practitioners, external observers and \acp{DM}. Furthermore, its simplicity and a priori obviousness is a strong point in its favor. It has, in some intuitive sense that cannot be described formally, less “content”, in the sense of that word used when economists argue that their theories should not have content about the preferences of the individuals (for fear of being paternalistic or dictatorial). Of course, any decision theory has content in a wider sense of imposing some structure to preferences, otherwise, the theory is void. The question is: are the restrictions imposed of a kind that can be judged acceptable with respect to the considered applications of the theory? Mandating, as is done here, that the judgments be of the sort that resists against counter-arguments seems to me to capture exactly what is desired in a prescription context.
%Arguably, the normative axiom proposed here is much weaker than those of a theory such as \ac{SEU}, in the sense of having less substance. (This claim can only be valid at an intuitive level: because \ac{SEU} does not use arguments, its axioms cannot be compared formally to mine.) 
The lack of concrete substance in its axiom does not prevent theories of \ac{DJ} to propose substantive, non-trivial claims about reflective preferences. It simply moves the debate from the world of discussions between experts about the validity of the axioms to the world of observations of acceptability of arguments by the persons to which these theories claim to be applicable.
It is also worth noting that the proposed axiom has a specific form that may permit decision makers to reconstruct the reasoning proposed by the theory so as to be able to check that they apply to their situation. Detailed exploration of this aspect is deferred to future work.

The rest of this article is structured as follows.
\Cref{sec:approaches} defines more precisely what is meant here with normative and descriptive theories. These definitions permit to readily see why the apparent impossibility of a claim being both normative and descriptive is an illusion, thereby enabling a solution to what could be called the “normative against descriptive” gap. It also reviews related works in the literature, and briefly sketches the current proposal.
\Cref{sec:normative,sec:descriptive} define the theories of \ac{DJ} and prove that these theories are normative and descriptive in the sense defined in \cref{sec:approaches}. \Cref{sec:preferences} define theories of \ac{DP} on the basis of theories of \ac{DJ}, and \cref{sec:conclusion} concludes.

@@

@@

\section{Descriptive theories}
\label{sec:descriptive}
\subsection{Informal presentation}
\commentOCf{Je ne me suis pas encore décidé : descriptive theory or empirical theory ? Pour le moment, j’utilise les deux expressions de façon interchangeable.}
A normative theory defines when a given argument is decisive for a given proposition and a given individual: whenever every sequence of arguments having that argument towards the end of the sequence lead the individual to adhere to the proposition. This, in turn, under condition of accepting its normative validity \commentYM{mais c'est quoi cette "normative validiy" ? de quelles conditions parles-tu ?}, permits in principle to know something about the \ac{DJ} of an individual. But this gives no concrete means to know someone’s \ac{DJ}. The set of finite sequence of arguments is infinite. The definition of decisiveness could admittedly be modified to account for an a priori bound on the maximal length of sequences, but this would not solve the practical problem that this set would be too large to be explored thoroughly 
\commentYM{certain que ce terme existe ?}
\commentOCf{Non, thoroughfully n’existe pas, en effet}. 
Furthermore, only some sequences of arguments can be tested for a given individual: the individual’s patience is limited. A supplementary problem might happen in some situations. Once a sequence has been presented to the individual, this cannot necessarily be undone: she might remember some of the arguments, and they may have a lasting influence on her perspective. Let me call this possibility the hypothesis of memory.
The converse hypothesis amounts to postulating that the individual forgets after some time and use an observation protocol that separates the tests in time sufficiently.
\commentYM{je comprends ce que tu veux dire ici car ça fait un bout de temps qu'on parle de ces question. Je doute cependant qu'un lecteur innocent comprenne un traitre mot}
The hypothesis of memory further reduces the possible sequences that can be tested with a given individual.

Achieving knowledge of someone’s \ac{DJ} in practice is tackled by introducing empirical theories of \ac{DJ}. An empirical theory for a given normative theory defines a subset of propositions of the agenda, that it claims are contained in the \acp{DJ} of individuals concerned by the normative theory. They are called the proposition that the theory supports. \commentYM{dans la mesure où, à ce stade, je ne comprends pas bien ce que contient une "normative theory", la séparation avec l' "empirical theory" n'est pas claire pour moi} 
%The theory also claims that it is able to argue in favor of the proposition it supports in such a way that individuals will be convinced of the quality of these arguments. This is accomplished by three binary relations, part of the definition of empiricial theories: one represents its initial arguments, one plans the possible attacks, and one defines its counter-arguments. An empirical theory also defines a concatenation operation able to dynamically build arguments from fragments of arguments.
%The theory claims that when one of its arguments in support of one of its claims is unconvincing to an individual, it is because of one of the anticipated attacks; and the theory claims to be able to provide counter-arguments to such attacks as they come, that will in turn be either convincing to the individual, or fail to be because of some anticipated attack. The theory is also constrained to have “finite depth”, meaning that it must set an a priori limit to the number of such iterations of attacks and counter-arguments.

%Thanks to these operators, an empirical theory may argue in a way that depends on the counter-arguments each individual finds appealing
%\commentYM{je ne comprends pas cette phrase, et en particulier le sens qu'il faut donner au terme "adjust"}. Instead of having to give a single decisive argument in support of its claims, the theory may react to exactly the counter-arguments that a given individual thinks relevant.

Such theories satisfy the two properties that are mandatory to achieve what has been announced, namely, to obtain theories of \ac{DJ} whose power rest on a weak normative axiom and on empirically falsifiable claims. First, the claim of the theory that it argues convincingly holds if and only if no falsification sequence exist (falsification sequences are defined formally here below). Second, granted normative adequacy, if indeed a theory argues convincingly, then it is valid, meaning that the proposition that it claims are \acp{DJ} are indeed \acp{DJ}. These two claims are laid out formally in \cref{th:svalid}.

A second goal of this section is to prove that when two theories disagree about incompatible propositions, one of the theories at least must fail some given sequence of empirical tests, which the proof describes. Importantly, these tests can be performed on a single individual and are robust against the hypothesis of memory.

\subsection{Definition}
In this section, a normative theory of \ac{DJ} $(\allprops, \allargs, I, {\allleadsto})$ is supposed given.
A descriptive tuple for a normative theory of \ac{DJ} is defined as a tuple $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$, where ${\gleadsto} \subseteq \allargs × \allprops$ is an initial argumentation relation; ${\gbeats} \subseteq \allargs × \allargs$ is an anticipated attacks relation; $\alldargs$ is a primitive set of argument fragments; ${\dbeats} \subseteq \alldargs × \gbeatsinv(\allargs)$ is a defense relation; and $+$ combines arguments to coalitions of fragments in order to form new arguments.
A descriptive theory for a normative theory of \ac{DJ} is a descriptive tuple that has a bounded depth.
These concepts are now defined formally.
\commentYM{puisque la théorie empirique est une théorie empirique D'UNE CERTAINE THEORIE NORMATIVE, je m'attendrais  à ce qu'on voit apparaître la théorie normative dans la formule de la théorie empirique, non ?}

An initial argumentation relation ${\gleadsto} \subseteq \allargs × \allprops$ defines the set of supported  propositions and, for each supported propositions, the set of initial arguments for these propositions. 
More precisely, let $\gpropse$, the range of ${\gleadsto}$, be called the propositions \emph{supported} by the descriptive theory.
Given such a supported proposition $\prop \in \gpropse$, let $\gleadstoinv(\prop) = \set{\ar \in \allargs \suchthat \ar \gleadsto \prop}$ be called the initial arguments in favor of $\prop$.

@@

A defense relation ${\dbeats} \subseteq \alldargs × \gbeatsinv(\allargs)$ is an injective (left-unique) and surjective (right-total) binary relation over $\alldargs × \gbeatsinv(\allargs)$. \commentYM{le fait qu'elle soit surjective et injective est une exigence que tu poses dans la définiton ? pourquoi ? à quoi est-ce que cela sert ?} 
These constraints guarantee that every anticipated attack has exactly one fragment defending against it, thus, $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton. 
Note that $\dbeats$ need not be a bijection as it is generally not a function (it is not restrictive to suppose it left-total, but it generally is not right-unique). 
Given $\ar_1 \in \gbeatsinv(\allargs)$, define $\dbeatsinv(\ar_1)$ as the fragment defending against the anticipated attack $\ar_1$.
\commentYM{dans toute cette sous-section la lecture est rendue très difficile par ce genre de formulation qui assigne une intentionnalité à la théorie. Je ne comprends pas le sens métaphorique de ces phrase, donc je ne les comprends pas}

@@

A \emph{coalition of fragments defending $\ar$} is any non-empty subset of $\df(\ar)$.
Such a coalition can be combined with the argument it defends to form a new argument.
An empirical theory defines, to that effect, a function $+: \allargs × \powersetz{\alldargs} → \allargs$.
Given any $\ar \in \allargs$ and $\emptyset ≠ \dargs \subseteq \alldargs$, the notation $\ar + \dargs$ stands for $+(\ar, \dargs)$. (The function $+$ need not be defined on so large a domain, because an argument is only ever added to its own defenders, but this definition is adopted here for simplicity; \cref{sec:append} refines this requirement.)
